Using \LaTeX\ to submit manuscripts to peer reviewed journals.

### 2014-03-04 docs/thesis/chap-cern_math_explorer.tex
Work on thesis doc: Added intro section and status of MIR.

The two functions that are more relevant for our work are {\codefont Simplify} and {\codefont FullySimplify} since they apply most of the other combined methods and do not require additional information.

Table \ref{table_simplifications} presents some sample equations found in some the documents in CDS and the different forms of simplification.

\begin{tabular}{|>{\centering\arraybackslash}m{4cm}|>
{\centering\arraybackslash}m{4cm}|>
{\centering\arraybackslash}m{4cm}|}
\hline
Original Form & {\codefont Simplify} & {\codefont FullSimplify} \\
\hline
\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mn>2</mn> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>+</mo> <mi>Φ</mi> </mrow> <mo>)</mo> </mrow> </mrow> </mfrac> <mo>+</mo> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> </mrow> <mo>=</mo> <mn>0</mn> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>Φ</mi> </mrow> <mo>+</mo> <mn>2</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>2</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mi>Φ</mi> <mo>+</mo> <mn>1</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}     \\
$\frac{\Phi '}{2 (1+\Phi )}+\frac{1}{r}=0$          & $\frac{1}{r}+\frac{\Phi '}{2 \Phi +2}=0$ & $\frac{2}{r}+\frac{\Phi '}{\Phi +1}=0$       \\

\hline
\end{tabular}

@@

\begin{figure}
\includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
\label{comparison_sw_table}
\caption{High level deployment architecture}
\end{figure}

@@

\begin{figure}
\includegraphics[height=8 cm]{figures/input_interface.png}
\label{comparison_sw_table}
\caption{Web interface of $5e^{x+y}$: Query input screen}
\end{figure}

\begin{figure}
\includegraphics[height=8 cm]{figures/results_interface.png}
\label{comparison_sw_table}
\caption{Web interface of $5e^{x+y}$: Results screen}
\end{figure}

>>>>

The two functions that are more relevant for our work are {\codefont Simplify} and {\codefont FullySimplify} since they apply a combination of the other methods and do not require additional information.

Table \ref{comparison_simplification} presents some sample equations found in some the documents in CDS and the different forms of simplification.

\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>
{\centering\arraybackslash}m{4.5cm}|>
{\centering\arraybackslash}m{4.5cm}|}
\hline
Original Form & {\codefont Simplify} & {\codefont FullSimplify} \\
\hline
\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mn>2</mn> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>+</mo> <mi>Φ</mi> </mrow> <mo>)</mo> </mrow> </mrow> </mfrac> <mo>+</mo> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> </mrow> <mo>=</mo> <mn>0</mn> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>Φ</mi> </mrow> <mo>+</mo> <mn>2</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>2</mn> <mi>r</mi> </mfrac> <mo>+</mo> <mfrac> <msup> <mi>Φ</mi> <mo>′</mo> </msup> <mrow> <mi>Φ</mi> <mo>+</mo> <mn>1</mn> </mrow> </mfrac> </mrow> <mo></mo> <mn>0</mn> </mrow> </math>}     \\
$\frac{\Phi '}{2 (1+\Phi )}+\frac{1}{r}=0$          & $\frac{1}{r}+\frac{\Phi '}{2 \Phi +2}=0$ & $\frac{2}{r}+\frac{\Phi '}{\Phi +1}=0$       \\

\hline

\scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mrow> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <mi>x</mi> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mrow> <mo>(</mo> <msup> <mi>e</mi> <mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </mrow> </msup> <mo>)</mo> </mrow> </mrow> </mrow> </math> }      & \scriptsize{\codefont <math> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mn>2</mn> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>-</mo> <mrow> <msub> <mi>i</mi> <mn>3</mn> </msub> <mo>⁢</mo> <mi>L</mi> </mrow> </mrow> <mo>)</mo> </mrow> </mrow> </math> }    & \scriptsize{\codefont <math> <mrow> <mrow> <mfrac> <mn>1</mn> <mn>2</mn> </mfrac> <mo>⁢</mo> <msup> <mi>x</mi> <mn>2</mn> </msup> <mo>⁢</mo> <mrow> <mi>log</mi> <mo>⁡</mo> <mo>(</mo> <mrow> <mn>1</mn> <mo>-</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> </mrow> <mo>)</mo> </mrow> </mrow> <mo>-</mo> <mrow> <mfrac> <mn>1</mn> <mn>4</mn> </mfrac> <mo>⁢</mo> <mi>L</mi> <mo>⁢</mo> <msup> <mi>e</mi> <mrow> <mrow> <mo>-</mo> <mn>2</mn> </mrow> <mo>⁢</mo> <mi>x</mi> </mrow> </msup> <mo>⁢</mo> <mrow> <mo>(</mo> <mrow> <mrow> <mn>2</mn> <mo>⁢</mo> <msub> <mi>i</mi> <mn>2</mn> </msub> <mo>⁢</mo> <mi>x</mi> </mrow> <mo>+</mo> <msub> <mi>i</mi> <mn>3</mn> </msub> </mrow> <mo>)</mo> </mrow> </mrow> </mrow> </math>}     \\ 
\scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right) - \frac{1}{2} x L i_ 2 \left(e^{-2 x}\right)-\frac{1}{4} L i_ 3 \left(e^{-2 x}\right)$ }          & \scriptsize { \begin{multline}  \frac{1}{4} e^{-2 x} (2 x^2 e^{2 x} \log (1-e^{-2 x})- \notag\\ 2 i_ 2 L x-i_ 3 L)  \end{multline} } & \scriptsize{ $\frac{1}{2} x^2 \log \left(1-e^{-2 x}\right)-\frac{1}{4} L e^{-2 x} \left(2 i_ 2 x+i_ 3\right)$ }      \\

\label{comparison_simplification}
\end{tabular}

@@

\begin{figure}
\includegraphics[height=4.2 cm]{visio_drawings/architecture.png}
\label{system_arch}
\caption{High level deployment architecture}
\end{figure}

@@

\begin{figure}
\includegraphics[height=8 cm]{figures/input_interface.png}
\label{input_interface}
\caption{Web interface of $5e^{x+y}$: Query input screen}
\end{figure}

\begin{figure}
\includegraphics[height=8 cm]{figures/results_interface.png}
\label{results_interface}
\caption{Web interface of $5e^{x+y}$: Results screen}
\end{figure}

### 2014-03-04 docs/thesis/chap-evaluation.tex
Work on thesis doc: Added intro section and status of MIR.

\chapter{Evaluation}
...

@@

The machine used for experiments has a Intel Core i7 processor running at 3.4Ghz with 4 cores. The available RAM is 8Gb, and the Java Virtual Machine used for running Solr was run with the $-Xms2G -Xmx5G$ parameters. The complete specifications of the used software is presented in table \ref{sw_used}

@@

We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain.

\section{Comparison against other systems}
In this section we compared our implementation of MASE(CDS) with the public available systems presented in the related work chapter. We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.  The systems were tested using Firefox 26.0
Table \ref{comparison_sw_table} presents the results of our test.

>>>>

\chapter{Evaluation}
When building an IR system there are two main aspects that should be considered. One is the quality of the presented results and the second one is the performance of the system since web users currently tolerate some milliseconds of latency for retrieving results.

@@

The machine used for experiments has a Intel Core i7 processor running at 3.4Ghz with 4 cores. The available RAM is 8Gb, and the Java Virtual Machine used for running Solr was run with the {\codefont -Xms2G -Xmx5G} parameters. The complete specifications of the used software is presented in table \ref{sw_used}

@@

We present results for three metrics: Partial precision (Document either partially relevant or completely relevant) strict precision and discounted cumulative gain ($ \mathrm{DCG_{p}} = \sum_{i=1}^{p} \frac{ 2^{rel_{i}} - 1 }{ \log_{2}(i+1)} $).

\section{Comparison against other systems}
In this section we compared our implementation of $5e^{x+y}$(CDS) with the public available systems presented in the related work chapter. We judged if the fetched results of each system were relevant or not using the same criteria as for the previous section.  The systems were tested using Firefox 26.0
Table \ref{comparison_sw_table} presents the results of our test.

### 2014-03-04 docs/thesis/chap-introduction.tex
work on document: added graphics
added section of dlmf
Work on thesis doc: Added intro section and status of MIR.

\section{CERN Document Server}

\section{Invenio}

>>>>

\section{Context}

\subsection{CERN}
CERN (Conseil Europ\'{e}en pour la Recherche Nucl\'{e}aire or European Organization for Nuclear Research)\cite{CERN}, founded in 1952, is the biggest research center in the area of particle physics. It is located in the French-Swiss border, near Geneva. Even though CERN directly employs around 2400 people, more than 10000 scientist from around 113 countries have visited CERN to deepen their research. As an example of its contributions to science, recently, in July of 2012, CERN announced that two different experiments (ATLAS and CMS) confirmed the existence of the particle named Higgs Boson, which lead to the award of the Nobel Prize to Peter Higgs and Fran\c{c}ois Englert.

Even though the main focus of CERN relies on the study of particle physics, the strong research environment has lead to important advances in several different areas, and one of the main inventions that CERN has contributed to the world is the Web. Tim Berners-Lee, in 1989, proposed a solution\cite{web_proposal} to the increasing problem of keeping track all the information related to the different experiments held at CERN, through a hypertext system.

\subsection{CDS Invenio}
CDS\cite{CDS1} (CERN Document Server) Invenio is the integrated digital library system developed and used at CERN\cite{CDS2}. To the date, it contains more than one million records and more than 400000 full-text documents. It provides tools to manage the complete workflow of a document taking care of the submission, annotation, edition, storage, searching, retrieval, displaying among other phases. Figure \ref{cds_screenshot} presents the search results for a simple query in CDS.

\begin{figure}
\centering
\includegraphics[height=7 cm]{figures/cds_screenshot.png}
\label{cds_screenshot}
\caption{CDS search result interface}
\end{figure}

Invenio\cite{invenio} is the software running behind CDS and is an open source project developed in parallel to CDS at CERN. Besides CDS, Invenio also supports around thirty scientific institutions worldwide including Fermilab, SLAC National Laboratory, INSPIRE and EPFL. 
Invenio is composed of several modules where each one can be mapped to a specific step in the workflow of a record. Figure \ref{invenio_architecture} presents the global architecture of Invenio. A detailed explanation of each module can be accessed in\cite{invenio_modules}

\begin{figure}
\centering
\includegraphics[height=10 cm]{figures/invenio.jpeg}
\label{invenio_architecture}
\caption{Invenio global architecture}
\end{figure}

\section{Project overview}
\subsection{Motivation}
The initial statement for this project was more generic and was encompassed as New ways to programmatically, accurately and efficiently extract data and metadata from digital files. During a first exploration around this topic, we focused our attention to the mathematical content that is stored in these files. After more discussions we identified that the extraction, storage, indexing and finally searching for mathematical content would be an and very useful project for CDS and an interesting research direction. CDS groups records in different categories or Collections such as Published Articles, Preprint, Photos, Books, General Talks among others. Some of these collections contain scientific documents in all of the different research areas where CERN is involved, and therefore a big amount of mathematical expressions are contained there. Only the Preprints collection contains 698581 records to the date, which harvest documents from services like ArXiV\cite{arxiv} where most of the documents are in the areas of physics, mathematics and statistics which are very rich in mathematical content.
Currently Invenio provides different ways of searching for records by specifying metadata fields like author:"Albert Einstein" or by keywords. However, there is no way to search for a given mathematical expression. The current workarounds would be to try to search for the name of the given expression if it is common enough to have been named like \emph{Schr\"oodinger equation}. This approach most of the times is not enough since most of the equations are not named and even named ones can be rewritten in several ways and each one may have a different importance to the user. This combination of factors, motivates the development of a complete system that allows users to search for relevant documents, based on mathematical expressions.

\subsection{Goals}

The specific goals of this project can be summarized as:

\begin{itemize}
\item Explore ways to automatically extract the mathematical content from a document collection
\item Investigate different approaches and formats to store mathematical expressions
\item Identify relevant features in a mathematical expression and how to use them to index equations
\item Using the created index, propose ways to efficiently retrieve relevant expressions and articles given an input query
\item Implement the previous steps into a complete system (A search engine) and integrate it into the Invenio software
\item Evaluate different approaches and the quality of the provided results
\item Identify deficiencies in our work and propose solutions and further direction on work
\end{itemize}

### 2014-03-04 docs/thesis/chap-related_work.tex
Added more characters/categories. Work on document: some drawings, graphics, and added comparison on simplification methods.
Work on thesis doc: Added intro section and status of MIR.

\chapter{Related Work}
\label{chapter-related_work}
\section{Status of MIR}
\subsection{TREC}
\subsection{TREC}
\subsection{CLEF}
\subsection{NTCIR}
\section{Mathematical based search projects}
\subsection{MIaS}
MIaS\cite{mias_1} (Math Indexer and Searcher), currently, is one of the flagship projects in the indexing and searching of mathematical content. As most of the other projects, it processes documents in MathML format. It allows the user to include in the queries mathematical expressions and textual content. During indexing time, equations are transformed following a set of heuristics that include:
\begin{itemize}
  \item Ordering of elements: Taking into account commutativity of certain operators (Addition, multiplication), elements are ordered such that $3 + a$ would be converted into $a + 3$ (Since the <mi> tag comes first than the <mn> tag)
  \item Unification of variables: This process takes into the account the structure of the equations in despite of the naming of the variables. Expressions like $a+b^a$ and $x+y^x$ would be converted into an expressions of the form $id_1 + id_2^{id_1}$ which would match.
  \item Unification of constants: This step consists of replacing all occurrences of constants (<mn> tags) by a const symbol. 
\end{itemize}
The extracted tokens from a given equation consist of all its valid sub-expressions. The original expression is given a weight value of 1, and following sub-expressions are given smaller weights depending on how general or specific they are.  
The system, also as most of the current projects, is developed by using the Apache Lucene framework. The system adapts the default scoring equation such that the given weight is taken into account.  
\subsection{EgoMath}
EgoMath\cite{egomath1} and its new version EgoMath$^2$\cite{egomath2}, is a system oriented to index the mathematical content from the Wikipedia.org database. The processing steps before indexing are similar to the ones in MIaS (Rearranging of symbols, unification of constants). The extraction process started from a complete dump of the Wikipedia database and filtering only the math articles, which are identified by the ”<math>" tag. This consists on around thirty thousand articles, from which 240.000 equations were identified. The processing step includes translating the equation from LaTeX into MathML format and then indexing both representation.
Some additional effort is done into splitting large mathematical blocks like tables into single mathematical expressions.

\subsection{DLMFSearch}
The Digital Library for Mathematical Funtions \cite{dlmf} is a project launched by the National Institute of Standards and Technology, in 2010, as an online version of the  Handbook of Mathematical Functions with Formulas, Graphs and Mathematical Tables\cite{handbook}. DLMF's main goal is to compile the mathematical knowledge in the form of equations, functions, tables and make this information useful for researchers and public in general. The system contains a search functionality that allows to input a combination of full text and \LaTeX snippets. The system tries to perform an exact match, and if no results are found, it relaxes the query. DLMF also perfoms some normalization of the equation and some cleaning of some characters, but no further details are provided. The content indexed by this project is highly curated, which differentiates it from the other projects. In the report published in 2013 \cite{dlmf2}, it is reported to have indexed around 38000 equations.

\subsection{MathWebSearch}
MathWebSearch\cite{mathwebsearch} (Currently on its 0.5 version) is a open-source search engine for mathematical equations. While most of the documentation relates on the architecture of the system and how they address scalability; the indexing technique is also very interesting. The system implements and idea proposed by Peter Graf in \cite{substitution_tree_indexing} called substitution tree indexing. This idea can be viewed as a generalization of the variable and constant unification. It represents the equations as a tree an recursively generalizes each sub-expression.

@@

\section{Other related projects and initiatives}
\subsection{arXMLiv}
\thispagestyle{empty}

>>>>

\chapter{Related Work}
\label{chap-related_work}
\section{Status of Mathematical Information Retrieval}
Even though Information Retrieval has been a research field from around the 1950s where the first metrics for such systems were developed and in the 1960s where SMART (System for Mechanical Analysis and Retrieval of Text), the first computer based system was developed; only in the last couple years focus have been put into adapting the same techniques to mathematical content.

The Mathematics Information Retrieval Workshop\cite{mir_worksop} held in the context of the Conference of Intelligent Computer Mathematics in July 2012, was the first official event in the area of MIR. Here, a small competition was held to evaluate different systems and approaches.

The NII\cite{nii} (National Institute of Informatics) is a Japanese research institute that hosts the project named NTCIR (NII Testbeds and Community for Information access Research) which aims to build evaluation frameworks for specific sub-fields of information retrieval. On 2013, in the context of the 10th NTCIR conference, it hosted the NTCIR-10 Math Task \cite{math_task} which was the first collaborative effort to evaluate different systems. The Math task was focused on two different subtasks: Math retrieval (Identifying relevant document based on given mathematical expressions and/or keywords) and Math understanding where the idea was to extract natural language information of a mathematical expression in a document. Currently submissions are open for the NTCIR-11 Math Task 2 which will be held on December 2014.

\section{Mathematical based search projects}

\subsection{MIaS}
MIaS\cite{mias_1} (Math Indexer and Searcher), currently, is one of the flagship projects in the indexing and searching of mathematical content. As most of the other projects, it processes documents in MathML format. It allows the user to include in the queries mathematical expressions and textual content. During indexing time, equations are transformed following a set of heuristics that include:
\begin{itemize}
  \item Ordering of elements: Taking into account commutativity of certain operators (Addition, multiplication), elements are ordered such that $3 + a$ would be converted into $a + 3$ (Since the <mi> tag comes first than the <mn> tag)
  \item Unification of variables: This process takes into the account the structure of the equations in despite of the naming of the variables. Expressions like $a+b^a$ and $x+y^x$ would be converted into an expressions of the form $id_1 + id_2^{id_1}$ which would match.
  \item Unification of constants: This step consists of replacing all occurrences of constants (<mn> tags) by a const symbol. 
\end{itemize}
The extracted tokens from a given equation consist of all its valid sub-expressions. The original expression is given a weight value of 1, and following sub-expressions are given smaller weights depending on how general or specific they are.  
The system, also as most of the current projects, is developed by using the Apache Lucene framework. The system adapts the default scoring equation such that the given weight is taken into account.  
Publicly available instances of the system can be found at: \url{http://aura.fi.muni.cz:8085/webmias/ps?n=-1} running on the MREC\cite{mrec} dataset and  \url{ http://aura.fi.muni.cz:8085/webmias-ntcir/} (Running on the NTCIR dataset)

\subsection{EgoMath}
EgoMath\cite{egomath1} and its new version EgoMath$^2$\cite{egomath2}, is a system oriented to index the mathematical content from the Wikipedia.org database. The processing steps before indexing are similar to the ones in MIaS (Rearranging of symbols, unification of constants). The extraction process started from a complete dump of the Wikipedia database and filtering only the math articles, which are identified by the ”<math>" tag. This consists on around thirty thousand articles, from which 240.000 equations were identified. The processing step includes translating the equation from LaTeX into MathML format and then indexing both representation.
Some additional effort is done into splitting large mathematical blocks like tables into single mathematical expressions. At the start of this work, EgoMath was publicly available at \url{http://egomath.projekty.ms.mff.cuni.cz/}, however at this moment the system seems to be unavailable.

\subsection{DLMFSearch}
The Digital Library for Mathematical Funtions \cite{dlmf} is a project launched by the National Institute of Standards and Technology, in 2010, as an online version of the  Handbook of Mathematical Functions with Formulas, Graphs and Mathematical Tables\cite{handbook}. DLMF's main goal is to compile the mathematical knowledge in the form of equations, functions, tables and make this information useful for researchers and public in general. The system contains a search functionality that allows to input a combination of full text and \LaTeX snippets. The system tries to perform an exact match, and if no results are found, it relaxes the query. DLMF also perfoms some normalization of the equation and some cleaning of some characters, but no further details are provided. The content indexed by this project is highly curated, which differentiates it from the other projects. In the report published in 2013 \cite{dlmf2}, it is reported to have indexed around 38000 equations. This project is publicly available at \url{http://dlmf.nist.gov/}

\subsection{MathWebSearch}
MathWebSearch\cite{mathwebsearch} (Currently on its 0.5 version) is a open-source search engine for mathematical equations. While most of the documentation relates on the architecture of the system and how they address scalability; the indexing technique is also very interesting. The system implements and idea proposed by Peter Graf in \cite{substitution_tree_indexing} called substitution tree indexing. This idea can be viewed as a generalization of the variable and constant unification. It represents the equations as a tree an recursively generalizes each sub-expression. A public available instance of the system is available at \url{http://search.mathweb.org/tema/} which runs on the Zentralblatt Math database\cite{zb}.

@@

Other systems that provide similar search functionalities are \url{Uniquation} and \url{http://www.symbolab.com/}, however detailed information about the systems are not provided. Finally Wolfram Alpha\cite{wolframalpha} is a very powerful tool that allows to find information about lots of mathematical concepts and a wide variety of other objects (Even pokemons).
